### 2017-05-26 Blog/04-LagrangianSubsetOfHamiltonian.tex
Final review before posting

TL;DR Lagrangians must be convex while Hamiltonians may not. Lagrangian systems are Hamiltonian systems where the momentum is a function $p=p(x,v)$ of position and velocity, strictly increasing with respect to velocity.

@@

We'll see that all the Lagrangians that lead to solvable equations of motion admit a Hamiltonian (i.e. they must be convex/hyper-regular) but not all Hamiltonians that lead to solvable equations of motions admit a Lagrangian (i.e. they may not be convex/hyper-regular). This means that every Lagrangian system is also a Hamiltonian system, but not vice-versa.

@@

This is a set of ordinary differential equations so the Picard Lindelöf theorem applies: if the right side is Lipschitz continuous then the solution exists and it is unique. But the right side are just the derivatives of $H$, which are differentiable because we assumed $H$ is twice differentiable. All differentiable functions are Lipschitz continuous therefore if $H$ is twice differentiable the initial value problem is always defined.

This means: the Hamiltonian does not have to be convex. In fact, we can set the Hamiltonian to be zero (i.e. $H=0$): we simply get $x(t)=x_0$ and $p(t)=p_0$. Contrast this with setting the Lagrangian to zero. The action for all paths would be equal to $0$, all paths minimize it: there is no unique solution.

@@

An intuitive way to remember this: Lagrangian systems are those Hamiltonian system for which each state can be recognized just by looking at its trajectory. If two states have the same trajectory (e.g. the velocity of a photon is always the same no matter the magnitude of momentum) then the system is not Lagrangian.

>>>>

TL;DR Lagrangians must be convex while Hamiltonians may not. Lagrangian systems are Hamiltonian systems where the momentum is a function $p=p(x,v)$ strictly increasing with respect to velocity (i.e. an increase in momentum yields an increase in velocity).

@@

What happens is that that all the Lagrangians that lead to solvable equations of motion admit a Hamiltonian (i.e. they must be convex/hyper-regular) but not all Hamiltonians that lead to solvable equations of motions admit a Lagrangian (i.e. they may not be convex/hyper-regular). This means that every Lagrangian system is also a Hamiltonian system, but not vice-versa.

@@

This is a set of ordinary differential equations so the Picard Lindelöf theorem applies: if the right side is Lipschitz continuous then the solution exists and it is unique. But the right side are just the derivatives of $H$, which are differentiable because we assumed $H$ is twice differentiable. All differentiable functions are Lipschitz continuous therefore if $H$ is twice differentiable the equations have a unique solution.

This means: the Hamiltonian does not have to be convex. In fact, we can set the Hamiltonian to be zero (i.e. $H=0$): we simply get $x(t)=x_0$ and $p(t)=p_0$. The Legendre transformation would give a zero Lagrangian (i.e. $L=0$). The action for all paths would be equal to $0$, all paths minimize it: there is no unique solution.

@@

An intuitive way to remember this: Lagrangian systems are those Hamiltonian system for which each state can be recognized just by looking at its trajectory. If two different states have the same trajectory (e.g. the velocity of a photon is always the same no matter the magnitude of momentum) then the system is not Lagrangian.
